---
title: "R Notebook"
output: html_notebook
---

# LoadPackages
```{r}
library(openxlsx)
library(readr)
library(irr)
library(openxlsx)
library(caret)
library(glmnet)
library(MASS)
library(ggplot2)
library(survival)
library(Hmisc)
library(ROSE)
library(survminer)
library(compareGroups)

library(pROC)

library(gcookbook)
library(OptimalCutpoints)
library(ggpubr)
library(showtext)

font_add('Araial','/Library/Fonts/Arial.ttf')

windowsFonts(A=windowsFont("Araial")) 
rm(list = ls())



```

# 1.1 Fature Bind: LiuYuan 
```{r}
rm(list = ls())
feature_DWI <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/LiuYuan_RadiomicsFeature_DWI.xlsx", sheet=1)
feature_T2 <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/LiuYuan_RadiomicsFeature_T2.xlsx", sheet=1)
feature_CLI <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/LiuYuan_Fix.xlsx", sheet=1)

feature_CLI <- feature_CLI[feature_CLI$group==0,]
feature_CLI[,2] <- as.numeric(unlist(feature_CLI[,2]))
feature_DWI[,1]<- as.numeric(unlist(feature_DWI[,1]))
feature_T2[,1] <- as.numeric(unlist(feature_T2[,1]))

ALL <- data.frame(feature_DWI, feature_T2)
feature_All <- merge(ALL, feature_CLI, by="patientname")
Feature_LiuYuan <- feature_All
Feature_LiuYuan$group <- 'LiuYuan'

```

# 1.2 Fature Bind: SanYuan
```{r}
feature_DWI <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/SanYuan_RadiomicsFeature_DWI.xlsx", sheet=1)
feature_T2 <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/SanYuan_RadiomicsFeature_T2.xlsx", sheet=1)
feature_CLI <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/SanYuan_Fix.xlsx", sheet=1)

feature_CLI <- feature_CLI[feature_CLI$group==0,]
feature_CLI[,2] <- as.numeric(unlist(feature_CLI[,2]))
feature_DWI[,1]<- as.numeric(unlist(feature_DWI[,1]))
feature_T2[,1] <- as.numeric(unlist(feature_T2[,1]))

ALL <- data.frame(feature_DWI, feature_T2)
feature_All <- merge(ALL, feature_CLI, by="patientname")
Feature_SanYuan <- feature_All
Feature_SanYuan$group <- 'SanYuan'

```

# 1.3 Fature Bind: YunNan
```{r}
feature_DWI <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/YunNan_RadiomicsFeature_DWI.xlsx", sheet=1)
feature_T2 <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/YunNan_RadiomicsFeature_T2.xlsx", sheet=1)
feature_CLI <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/YunNan_Fix.xlsx", sheet=1)

feature_CLI <- feature_CLI[feature_CLI$group==0,]
feature_CLI[,2] <- as.numeric(unlist(feature_CLI[,2]))
feature_DWI[,1]<- as.numeric(unlist(feature_DWI[,1]))
feature_T2[,1] <- as.numeric(unlist(feature_T2[,1]))

ALL <- data.frame(feature_DWI, feature_T2)
feature_All <- merge(ALL, feature_CLI, by="patientname")
Feature_YunNan <- feature_All
Feature_YunNan$group <- 'YunNan'

```

# 1.4 Save Feature_Bind
```{r}

Feature_All <- rbind(Feature_LiuYuan, Feature_SanYuan, Feature_YunNan)
Feature_All$agegroup <- ifelse(Feature_All$age < 50, "<50", ">=50")

write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Bind.xlsx")

```


# 2.1 ICC Index
```{r}
rm(list = ls())
feature_1 = read.xlsx("E:/Qian/ProjectAGE/Data/Data_Excel/ICC_org/Data_ICC.xlsx",sheet=1 )
feature_2 = read.xlsx("E:/Qian/ProjectAGE/Data/Data_Excel/ICC_org/Data_ICC.xlsx",sheet=2 )

len = length(names(feature_1))
icc_val <- vector(length=len)
thr <- 0.75
icc_val<-vector(length=len)
for (i in 1:len){
  rating <- cbind(as.numeric(feature_1[,i]),as.numeric(feature_2[,i]))
  icc_vals <- icc(rating, 
                 model='twoway', type='agreement', unit='single',
                 r0=0, conf.level=0.95)
  icc_val[i] <- icc_vals$value
 
}
icc_val[c(1:37, 1256:1293)] <- 0

index <- which(icc_val >= thr)
length(index)


dim(icc_val)=c(1,len)
icc_val_save <- icc_val
icc_val_save [icc_val_save < thr] <- 0
icc_val_save [icc_val_save >= thr] <- 1
write.csv(icc_val_save,file = "E:/Qian/ProjectAGE/Data/Data_Excel/ICC_org/Data_ICC_value.csv",row.names = F)

```

# 2.2 Save ICC Feature
```{r}
# Load Data
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Bind.xlsx", sheet=1) # 手动调整第一列

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Index_ICC <- which(icc_val_save == 1)
Feature_IMG <- Feature_All[, Index_IMG]
Feature_CLI <- Feature_All[, Index_CLI]

Feature_IMG <- Feature_IMG[, Index_ICC]

# Save Result
Feature_All <- data.frame(Feature_IMG, Feature_CLI)
write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_ICC.xlsx")

```

# 3 Split Data
```{r}
rm(list = ls())
set.seed("312") 
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_ICC.xlsx", sheet=1)# 手动排序
MRI_date <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/MRI_date.xlsx", sheet=1)
Feature_All <- Feature_All[-c(1,5,7,8,197, 308,309,311,313,336,337,340,343,360,362,363,
                      126,301,306,315,430,893),]

Index_LORC <- which(Feature_All$agegroup == ">=50")
Index_EORC <- which(Feature_All$agegroup == "<50")

Feature_LORC <- Feature_All[Index_LORC, ]
Feature_EORC <- Feature_All[Index_EORC, ]

Index_LiuYuan <- which(Feature_EORC$group == "LiuYuan" )
Index_TestExt <- which(!(Feature_EORC$group == "LiuYuan"))

# mydata <- Feature_All[Index_LiuYuan, ]#

tmp <- Feature_EORC[Index_LiuYuan, ]
tmp_data <- merge(tmp,MRI_date, by="patientname")
n1=65
n2=nrow(tmp)
Index_Train <- order(tmp_data$time)[1:(n2-n1)]
Index_TestInt <- order(tmp_data$time)[(n2-n1+1):n2]

Feature_LORC$Split <- "LORC"
Feature_EORC$Split <- "EORC"
Feature_EORC[Index_Train, ]$Split <- "Train"
Feature_EORC[Index_TestInt, ]$Split <- "TestInt"
Feature_EORC[Index_TestExt, ]$Split <- "TestExt"

Feature_All <- rbind(Feature_LORC, Feature_EORC)

write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Split.xlsx")

```


# 4 Difference Analysis
# 4.1.1 Load Data
```{r}
rm(list = ls())
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Split.xlsx", sheet=1) 

Feature_All$agegroup <- ifelse(Feature_All$age <50, "<50", ">=50")

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Feature_IMG <- apply(Feature_All[,Index_IMG], 2, as.numeric)
Feature_CLI <- Feature_All[, Index_CLI]

Feature_Violin <- Feature_All

```


# 4.1.2 Wilcox_test
```{r}

number <- ncol(Feature_IMG) # N是特征的数量

thr <- 0.05
testresult<-vector(length=number)
age_group <- Feature_All$agegroup

for (i in 1:number){
  tmpresult <- wilcox.test(as.numeric(Feature_IMG[,i])~age_group, data=Feature_IMG)
  testresult[i] <- tmpresult$p.value
}

Index <- which(testresult < thr)
length(Index)

Feature_IMG <- Feature_IMG[,Index]
colnames(Feature_IMG)

write.csv(t(colnames(Feature_IMG)), "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Diff_feature_name.csv")


Feature_All <- data.frame(Feature_IMG, Feature_CLI)
write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Diff.xlsx")

```

```{r}
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Diff.xlsx", sheet=1)
library(gtsummary)
mydata <- Feature_All
res_tab <- descrTable(agegroup~., data = mydata, show.all = TRUE, digits = 2, method =  NA)
res_tab
export2xls(res_tab, file="E:/Qian/ProjectAge/Data/Data_Excel/Table_df.xlsx")


a <- mydata %>% tbl_summary(by = agegroup) %>% add_p() %>% add_overall()
a
```

# 4.2.1 Load Diff Feature
```{r}
rm(list = ls())
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Diff.xlsx", sheet=1)
#Feature_All <- Feature_All[Feature_All$agegroup == "<50", ]

nume <- c("OS", "DFS")
Feature_All[nume] <- lapply(Feature_All[nume], as.numeric)

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Feature_IMG <- apply(Feature_All[,Index_IMG], 2, as.numeric)
Feature_CLI <- Feature_All[, Index_CLI]

Index_Train <- which(Feature_All$Split == "Train")
Index_TestInt <- which(Feature_All$Split == "TestInt")
Index_TestExt <- which(Feature_All$Split == "TestExt")

```

# 4.2.2 Scale
```{r}

Train_IMG <- Feature_IMG[Index_Train, ]
  
stand_scale <- preProcess(Train_IMG)  # 默认为scale， 即均值方差（X-MU)/STD
#stand_scale <- preProcess(Feature_IMG, method = "range")   # 最大最小归一化
Feature_IMG <- predict(stand_scale, Feature_IMG)

Feature_All <- data.frame(Feature_IMG, Feature_CLI)

```

# 4.2.3 Uni_Cox
```{r}
mydata <- Feature_All[Index_Train, ]
testresult<-vector(length = length(Index_IMG))
thr <- 0.05

# 1256_1293

IMG_num <- c(1:length(Index_IMG))
nume <- c("OS", "DFS")
mydata[nume] <- lapply(mydata[nume], as.numeric)

for (i in IMG_num){
  tmpresult <- coxph(Surv(DFSDAYS, DFS == 1)~mydata[,i], data = mydata)
  tmp <- summary(tmpresult)
  testresult[i] <- tmp[["waldtest"]][["pvalue"]]
}
Index <- which(testresult < thr)
length(Index)

Feature_IMG <- Feature_IMG[, Index]

feature_name_violine <- colnames(Feature_IMG)

```

# 4.2.4 Correction
```{r}

Train_IMG <- Feature_IMG[Index_Train, ]
  
Index_Cor <- findCorrelation(cor(Train_IMG, Train_IMG, method = "spearman" ),0.8)
colnames(Feature_IMG[,-Index_Cor])
Feature_IMG <- Feature_IMG[,-Index_Cor]
length(colnames(Feature_IMG))

Feature_All <- data.frame(Feature_IMG, Feature_CLI)

write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Diff_Cor.xlsx")

```


# 4.3.1 Load Data
```{r}
rm(list = ls())
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Diff_Cor.xlsx", sheet=1)

Feature_All[Feature_All$yT == "T0",]$yT <- "negative"
Feature_All[Feature_All$yT == "T1",]$yT <- "negative"
Feature_All[Feature_All$yT == "T2",]$yT <- "negative"
Feature_All[Feature_All$yT == "T3",]$yT <- "positive"
Feature_All[Feature_All$yT == "T4",]$yT <- "positive"

Feature_All$CEA_1 <- as.factor(ifelse(Feature_All$CEA_1 <=5,"negative", "positive"))

nume <- c("OS", "DFS")
Feature_All[nume] <- lapply(Feature_All[nume], as.numeric)

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Feature_IMG <- apply(Feature_All[,Index_IMG], 2, as.numeric)
Feature_CLI <- Feature_All[, Index_CLI]

Index_LORC <- which(Feature_All$Split == "LORC")
Index_Train <- which(Feature_All$Split == "Train")
Index_TestInt <- which(Feature_All$Split == "TestInt")
Index_TestExt <- which(Feature_All$Split == "TestExt")

```


# 4.3.2 Muti_Cox
```{r}

mydata <- Feature_All[Index_Train,]

tmp_y <- Surv(mydata$DFSDAYS, mydata$DFS == 1)
tmp_x <- names(mydata)[Index_IMG]
multi_formula <- as.formula(paste0 ("tmp_y~", paste0(tmp_x, collapse = "+")))
multi_formula

multi_models<- coxph(multi_formula, data =  mydata)
step_models <- stepAIC(multi_models, direction = "both")
summary(step_models)


coef_matrix <- as.data.frame(t(as.matrix(coef(step_models))))
#coef_matrix <- sort(coef_matrix,decreasing = T)[,1:5]
Feature_IMG <- Feature_IMG[, colnames(coef_matrix)]

```


# 4.3.3 Calculate RS
```{r}

data_train <- Feature_All[Index_Train,]

feature_final <- vector(mode="numeric", length=nrow(data_train ))
for (i in 1:length(coef_matrix)){
  tmp_coef <- as.numeric(coef_matrix[i])
  tmp_name <- colnames(coef_matrix)[i]
  temp_feature <- as.numeric(data_train [,c(tmp_name)])*tmp_coef
  feature_final <- feature_final+temp_feature
}

data_train$Riskscore <- feature_final
data_train$RS_median <- ifelse(data_train$Riskscore >= median(data_train$Riskscore), "high", "low")
RS_value <- median(data_train$Riskscore)
cutoff_value<-surv_cutpoint(data_train, time="DFSDAYS", event="DFS", variables="Riskscore")
data_train$RS_cutoff <- ifelse(data_train$Riskscore >= cutoff_value[["cutpoint"]][["cutpoint"]], 'high', 'low')

# calculate Riskscore
library(survminer)
Feature_All <- as.data.frame(Feature_All)
feature_final <- vector(mode="numeric", length=nrow(Feature_All ))
for (i in 1:length(coef_matrix)){
   tmp_coef <- as.numeric(coef_matrix[i])
   tmp_name <- colnames(coef_matrix)[i]
   temp_feature <- as.numeric(Feature_All[,c(tmp_name)])*tmp_coef
   feature_final <- feature_final+temp_feature
}

Feature_CLI$Riskscore <- feature_final
Feature_CLI$RS_median <- ifelse(Feature_CLI$Riskscore >= RS_value, 'high', 'low')
cutoff_value<-surv_cutpoint(data_train, time="DFSDAYS", event="DFS", variables="Riskscore")
Feature_CLI$RS_cutoff <- ifelse(Feature_CLI$Riskscore >= cutoff_value[["cutpoint"]][["cutpoint"]], 'high', 'low')

Feature_All <- data.frame(Feature_IMG, Feature_CLI)
write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Diff_Cox.xlsx")
# 
# showtext_auto(enable=T)
# pdf("cutoff_value.pdf")
# plot(cutoff_value, "Riskscore", palette = "lancet")
# while (!is.null(dev.list())) dev.off() 
# showtext_auto(enable=F)

```

# 4.3.4 C-Index
```{r}
# Riskscore


cindex_f <- function(mydata,tmp_formu,i){
  multi_models<- coxph(tmp_formu, data =  mydata)
  fp <- predict(multi_models, mydata)
  tmp_C=rcorr.cens(fp, Surv(mydata$DFSDAYS, mydata$DFS == 1))
  Cindex[i,1]  <- 1-tmp_C[1]
  Cindex[i,2] <- 1-tmp_C[1]-0.98*tmp_C[3]
  Cindex[i,3] <- 1-tmp_C[1]+0.98*tmp_C[3]
  Cindex[i,4] <- paste0(round(Cindex[i,1], digits = 2),"[",
                        round(Cindex[i,2], digits = 2),",",
                        round(Cindex[i,3], digits = 2),"]")
  return(Cindex)
  
  
}

Cindex <- data.frame()
tmp_formu <- as.formula('Surv(DFSDAYS, DFS == 1)~Riskscore')

i=1
mydata <- Feature_All[Index_Train, ]
Cindex <- cindex_f(mydata,tmp_formu, i)

i=2
mydata <- Feature_All[Index_TestInt, ]
Cindex <- cindex_f(mydata,tmp_formu, i)

i=3
mydata <- Feature_All[Index_TestExt, ]
Cindex <- cindex_f(mydata,tmp_formu, i)

i=4
mydata <- Feature_All[Index_LORC, ]
Cindex <- cindex_f(mydata,tmp_formu, i)

colnames(Cindex) <- c("Corcord", "Lower", "Upper","C-index")
row.names(Cindex) <- c("train", "testint", "testext","LORC")




Cindex <- data.frame()
tmp_formu <- as.formula('Surv(DFSDAYS, DFS == 1)~Riskscore+CEA_1+yN')

i=1
mydata <- Feature_All[Index_Train, ]
Cindex <- cindex_f(mydata,tmp_formu, i)

i=2
mydata <- Feature_All[Index_TestInt, ]
Cindex <- cindex_f(mydata,tmp_formu, i)

i=3
mydata <- Feature_All[Index_TestExt, ]
Cindex <- cindex_f(mydata,tmp_formu, i)

colnames(Cindex) <- c("Corcord", "Lower", "Upper","C-index")
row.names(Cindex) <- c("train", "testint", "testext")

```

# 5 EORC Analysis
# 5.1.1 Load Data
```{r}
rm(list = ls())
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Split.xlsx", sheet=1)
#Feature_All$agegroup <- ifelse(Feature_All$age <50, "<50", ">=50")
#Feature_All <- Feature_All[Feature_All$agegroup == "<50", ]


nume <- c("OS", "DFS")
Feature_All[nume] <- lapply(Feature_All[nume], as.numeric)

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Feature_IMG <- apply(Feature_All[,Index_IMG], 2, as.numeric)
Feature_CLI <- Feature_All[, Index_CLI]

Index_Train <- which(Feature_All$Split == "Train")
Index_TestInt <- which(Feature_All$Split == "TestInt")
Index_TestExt <- which(Feature_All$Split == "TestExt")

```

# 5.2.1 Scale
```{r}

Train_IMG <- Feature_IMG[Index_Train, ]
  
stand_scale <- preProcess(Train_IMG)  # 默认为scale， 即均值方差（X-MU)/STD
#stand_scale <- preProcess(Feature_IMG, method = "range")   # 最大最小归一化
Feature_IMG <- predict(stand_scale, Feature_IMG)

Feature_All <- data.frame(Feature_IMG, Feature_CLI)
#write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Scale.xlsx")

```



# 5.2.2 Uni_Cox
```{r}
mydata <- Feature_All[Index_Train, ]
testresult<-vector(length = length(Index_IMG))
thr <- 0.05

# 1256_1293

IMG_num <- c(1:length(Index_IMG))
nume <- c("OS", "DFS")
mydata[nume] <- lapply(mydata[nume], as.numeric)

for (i in IMG_num){
  tmpresult <- coxph(Surv(DFSDAYS, DFS == 1)~mydata[,i], data = mydata)
  tmp <- summary(tmpresult)
  testresult[i] <- tmp[["waldtest"]][["pvalue"]]
}
Index <- which(testresult < thr)
length(Index)

Feature_IMG <- Feature_IMG[, Index]

```

# 5.2.3 Correction
```{r}

Train_IMG <- Feature_IMG[Index_Train, ]
  
Index_Cor <- findCorrelation(cor(Train_IMG, Train_IMG, method = "spearman" ),0.8)
colnames(Feature_IMG[,-Index_Cor])
Feature_IMG <- Feature_IMG[,-Index_Cor]
length(colnames(Feature_IMG))

Feature_All <- data.frame(Feature_IMG, Feature_CLI)
write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Cor.xlsx")


# a <- cor(Train_IMG, Train_IMG)
# corrplot(a, method = "square", tl.cex = 0.6, tl.col = "black", cl.pos = "n", tl.pos="n",tl.srt = 45)
# 
# showtext_auto(enable=T)
# pdf("Table1.pdf")
# corrplot(a, method = "square", tl.cex = 0.6, tl.col = "black", cl.pos = "r", tl.pos="lt",tl.srt = 45)
# while (!is.null(dev.list())) dev.off() 
# showtext_auto(enable=F)

```

# 5.3.1 Load Data
```{r}
rm(list = ls())
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Cor.xlsx", sheet=1)

nume <- c("OS", "DFS")
Feature_All[nume] <- lapply(Feature_All[nume], as.numeric)

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Feature_IMG <- apply(Feature_All[,Index_IMG], 2, as.numeric)
Feature_CLI <- Feature_All[, Index_CLI]

Index_Train <- which(Feature_All$Split == "Train")
Index_TestInt <- which(Feature_All$Split == "TestInt")
Index_TestExt <- which(Feature_All$Split == "TestExt")

```



# 5.3.2 Muti_Cox
```{r}

mydata <- Feature_All[Index_Train,]

tmp_y <- Surv(mydata$DFSDAYS, mydata$DFS == 1)
tmp_x <- names(mydata)[Index_IMG]
multi_formula <- as.formula(paste0 ("tmp_y~", paste0(tmp_x, collapse = "+")))
multi_formula

multi_models<- coxph(multi_formula, data =  mydata)
step_models <- stepAIC(multi_models, direction = "both")
summary(step_models)


coef_matrix <- as.data.frame(t(as.matrix(coef(step_models))))
#coef_matrix <- sort(coef_matrix,decreasing = T)[,1:5]
Feature_IMG <- Feature_IMG[, colnames(coef_matrix)]

```



# 5.3.3 Calculate RS
```{r}

data_train <- Feature_All[Index_Train,]

feature_final <- vector(mode="numeric", length=nrow(data_train ))
for (i in 1:length(coef_matrix)){
  tmp_coef <- as.numeric(coef_matrix[i])
  tmp_name <- colnames(coef_matrix)[i]
  temp_feature <- as.numeric(data_train [,c(tmp_name)])*tmp_coef
  feature_final <- feature_final+temp_feature
}

data_train$Riskscore <- feature_final
data_train$RS_median <- ifelse(data_train$Riskscore >= median(data_train$Riskscore), "high", "low")
RS_value <- median(data_train$Riskscore)
cutoff_value<-surv_cutpoint(data_train, time="DFSDAYS", event="DFS", variables="Riskscore")
data_train$RS_cutoff <- ifelse(data_train$Riskscore >= cutoff_value[["cutpoint"]][["cutpoint"]], 'high', 'low')

# calculate Riskscore
library(survminer)
Feature_All <- as.data.frame(Feature_All)
feature_final <- vector(mode="numeric", length=nrow(Feature_All ))
for (i in 1:length(coef_matrix)){
   tmp_coef <- as.numeric(coef_matrix[i])
   tmp_name <- colnames(coef_matrix)[i]
   temp_feature <- as.numeric(Feature_All[,c(tmp_name)])*tmp_coef
   feature_final <- feature_final+temp_feature
}

Feature_CLI$Riskscore <- feature_final
Feature_CLI$RS_median <- ifelse(Feature_CLI$Riskscore >= RS_value, 'high', 'low')
cutoff_value<-surv_cutpoint(data_train, time="DFSDAYS", event="DFS", variables="Riskscore")
Feature_CLI$RS_cutoff <- ifelse(Feature_CLI$Riskscore >= cutoff_value[["cutpoint"]][["cutpoint"]], 'high', 'low')

Feature_All <- data.frame(Feature_IMG, Feature_CLI)
write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Cox.xlsx")

# showtext_auto(enable=T)
# pdf("cutoff_value.pdf")
# plot(cutoff_value, "Riskscore", palette = "lancet")
# while (!is.null(dev.list())) dev.off() 
# showtext_auto(enable=F)

```



# 6 RC Analysis
# 6.1.1 Load Data
```{r}
rm(list = ls())
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Split.xlsx", sheet=1)
#Feature_All$agegroup <- ifelse(Feature_All$age <50, "<50", ">=50")
#Feature_All <- Feature_All[Feature_All$agegroup == "<50", ]


nume <- c("OS", "DFS")
Feature_All[nume] <- lapply(Feature_All[nume], as.numeric)

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Feature_IMG <- apply(Feature_All[,Index_IMG], 2, as.numeric)
Feature_CLI <- Feature_All[, Index_CLI]

Index_Train <- which(Feature_All$Split_All == "Train")
Index_TestInt <- which(Feature_All$Split_All == "TestInt")
Index_TestExt <- which(Feature_All$Split_All == "TestExt")

```

# 6.2.1 Scale
```{r}

Train_IMG <- Feature_IMG[Index_Train, ]
  
stand_scale <- preProcess(Train_IMG)  # 默认为scale， 即均值方差（X-MU)/STD
#stand_scale <- preProcess(Feature_IMG, method = "range")   # 最大最小归一化
Feature_IMG <- predict(stand_scale, Feature_IMG)

Feature_All <- data.frame(Feature_IMG, Feature_CLI)
#write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Scale.xlsx")

```



# 6.2.2 Uni_Cox
```{r}
mydata <- Feature_All[Index_Train, ]
testresult<-vector(length = length(Index_IMG))
thr <- 0.05

# 1256_1293

IMG_num <- c(1:length(Index_IMG))
nume <- c("OS", "DFS")
mydata[nume] <- lapply(mydata[nume], as.numeric)

for (i in IMG_num){
  tmpresult <- coxph(Surv(DFSDAYS, DFS == 1)~mydata[,i], data = mydata)
  tmp <- summary(tmpresult)
  testresult[i] <- tmp[["waldtest"]][["pvalue"]]
}
Index <- which(testresult < thr)
length(Index)
#Index_rank <- rank(testresult[Index])

Feature_IMG <- Feature_IMG[, Index]

#Feature_IMG <- Feature_IMG[, Index_rank[c(1:68)]]

```

# 6.2.3 Correction
```{r}

Train_IMG <- Feature_IMG[Index_Train, ]
  
Index_Cor <- findCorrelation(cor(Train_IMG, Train_IMG, method = "spearman" ),0.8)
colnames(Feature_IMG[,-Index_Cor])
Feature_IMG <- Feature_IMG[,-Index_Cor]
length(colnames(Feature_IMG))

Feature_All <- data.frame(Feature_IMG, Feature_CLI)
write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Cor_All.xlsx")


# a <- cor(Train_IMG, Train_IMG)
# corrplot(a, method = "square", tl.cex = 0.6, tl.col = "black", cl.pos = "n", tl.pos="n",tl.srt = 45)
# 
# showtext_auto(enable=T)
# pdf("Table1.pdf")
# corrplot(a, method = "square", tl.cex = 0.6, tl.col = "black", cl.pos = "r", tl.pos="lt",tl.srt = 45)
# while (!is.null(dev.list())) dev.off() 
# showtext_auto(enable=F)

```

# 6.3.1 Load Data
```{r}
rm(list = ls())
Feature_All <- read.xlsx("E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Cor_All.xlsx", sheet=1)

nume <- c("OS", "DFS")
Feature_All[nume] <- lapply(Feature_All[nume], as.numeric)

nume <- as.numeric(which(names(Feature_All) == "patientname"))
Index_IMG <- c(1:(nume-1))
Index_CLI <- c(nume:length(Feature_All))

Feature_IMG <- apply(Feature_All[,Index_IMG], 2, as.numeric)
Feature_CLI <- Feature_All[, Index_CLI]

Index_Train <- which(Feature_All$Split_All == "Train")
Index_TestInt <- which(Feature_All$Split_All == "TestInt")
Index_TestExt <- which(Feature_All$Split_All == "TestExt")

```


```{r}
set.seed("12")
mydata <- Feature_All[Index_Train,]

tmp_y <- Surv(mydata$DFSDAYS, mydata$DFS == 1)
tmp_x <- mydata[, Index_IMG]


# no crDFSs validation alpha=1(LASSO) family=(binomial, gaussian)
model_lasso <-  glmnet(data.matrix(tmp_x), tmp_y, family="cox", nlambda=30, alpha=1)
plot(model_lasso,xvar="lambda",label=TRUE, cex.lab = 1.5, lwd=2)
model_lasso

# corss validation, type.measure=(mse, class, deviance)
glm_cv <- cv.glmnet(data.matrix(tmp_x), tmp_y, family="cox", type.measure = "C", 
                    nlambda=10, alpha=1, standardize=TRUE, nfolds = 3)

plot(glm_cv, cex.lab = 1.5, lwd=20)
glm_cv
coef(glm_cv, s=glm_cv$lambda.min)

#coef_matrix <- t(as.matrix(coef(glm_cv, s=glm_cv$lambda.min)))
coef_matrix <- t(as.matrix(coef(glm_cv, s=glm_cv$lambda.1se)))
Index_LASSO <- which(coef_matrix != 0)

coef_matrix <- t(coef_matrix[, Index_LASSO])
coef_matrix

Feature_IMG <- Feature_IMG[, Index_LASSO]
colnames(Feature_IMG)
length(colnames(Feature_IMG))


```




# 6.3.2 Muti_Cox
```{r}

mydata <- Feature_All[Index_Train,]

tmp_y <- Surv(mydata$DFSDAYS, mydata$DFS == 1)
tmp_x <- names(mydata)[Index_IMG]
multi_formula <- as.formula(paste0 ("tmp_y~", paste0(tmp_x, collapse = "+")))
multi_formula

multi_models<- coxph(multi_formula, data =  mydata)
step_models <- stepAIC(multi_models, direction = "both")
summary(step_models)

#[,c(6,7,8,10,16,18)]
coef_matrix <- as.data.frame(t(as.matrix(coef(step_models))))[,c(6,8,10,17,18)]
#coef_matrix <- sort(coef_matrix,decreasing = T)[,1:5]
Feature_IMG <- Feature_IMG[, colnames(coef_matrix)]

```

# 6.3.3 Calculate RS
```{r}

data_train <- Feature_All[Index_Train,]

feature_final <- vector(mode="numeric", length=nrow(data_train ))
for (i in 1:length(coef_matrix)){
  tmp_coef <- as.numeric(coef_matrix[i])
  tmp_name <- colnames(coef_matrix)[i]
  temp_feature <- as.numeric(data_train [,c(tmp_name)])*tmp_coef
  feature_final <- feature_final+temp_feature
}

data_train$Riskscore <- feature_final
data_train$RS_median <- ifelse(data_train$Riskscore >= median(data_train$Riskscore), "high", "low")
RS_value <- median(data_train$Riskscore)
cutoff_value<-surv_cutpoint(data_train, time="DFSDAYS", event="DFS", variables="Riskscore")
data_train$RS_cutoff <- ifelse(data_train$Riskscore >= cutoff_value[["cutpoint"]][["cutpoint"]], 'high', 'low')

# calculate Riskscore
library(survminer)
Feature_All <- as.data.frame(Feature_All)
feature_final <- vector(mode="numeric", length=nrow(Feature_All ))
for (i in 1:length(coef_matrix)){
   tmp_coef <- as.numeric(coef_matrix[i])
   tmp_name <- colnames(coef_matrix)[i]
   temp_feature <- as.numeric(Feature_All[,c(tmp_name)])*tmp_coef
   feature_final <- feature_final+temp_feature
}

Feature_CLI$Riskscore <- feature_final
Feature_CLI$RS_median <- ifelse(Feature_CLI$Riskscore >= RS_value, 'high', 'low')
cutoff_value<-surv_cutpoint(data_train, time="DFSDAYS", event="DFS", variables="Riskscore")
Feature_CLI$RS_cutoff <- ifelse(Feature_CLI$Riskscore >= cutoff_value[["cutpoint"]][["cutpoint"]], 'high', 'low')

Feature_All <- data.frame(Feature_IMG, Feature_CLI)
write.xlsx(Feature_All, "E:/Qian/ProjectAge/Data/Data_Excel/Data_org/Feature_Cox_All.xlsx")

# showtext_auto(enable=T)
# pdf("cutoff_value.pdf")
# plot(cutoff_value, "Riskscore", palette = "lancet")
# while (!is.null(dev.list())) dev.off() 
# showtext_auto(enable=F)

```
























